---
title: "Compostables"
output:
  html_document:
    fig_caption: true
    md_extensions: +link_attributes
    theme: null
    css: styles.css
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r images}
library(dplyr)
library(glue)

images <- tibble(path = fs::dir_ls("images", recurse = TRUE, type = "file")) %>%
  mutate(
    type = sub("^images/((not )?compostable)/.*$", "\\1", path),
    item = sub("[0-9]{1,2} - (.*)\\.(png|jpg)", "\\1", fs::path_file(path))
  ) %>%
  arrange(path) %>%
  split(x = ., f = .$type)

image_rows <- function(imgs) {
  template <- "<div class='item'>
  ![${item}](${path}){height=150px}
  <p class='caption'>${item}</p>
  </div>"
  floated <- imgs %>%
    transmute(graphic = glue(template, .open = "${")) %>%
    pull(graphic) %>%
    paste0(collapse = "\n")
  return(floated)
}
```

## `r emo::ji("check")` What to compost

```{r compostable, results='asis'}
cat(image_rows(images$compostable))
```

------

## `r emo::ji("x")` What not to compost

```{r not_compostable, results='asis'}
cat(image_rows(images$`not compostable`))
```

------

## How to compost

- Place food scraps in your bin druing food prep or after meals
- Once your countertop compost bin is full, do either:
  - Remove the waste (*with* your compostable bags) and toss in your yard trimmings garbage can.
  - If you have a composting area, your composting waste (*without* the bags) can also be discarded there.
- It is recommended that you replace your filter if you have a thick layer of mold growing on your filter.
  - If this is a continuing issue, you may need to adjust what you compost and how often you empty your bin.
  - Having your compost piled high in the bin so it touches the filter is not recommended and may aid in this issue as well.
